\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{hyphenat}
\usepackage{fontawesome}
\input{glyphtounicode}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}


\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeSubSubheading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeEducationHeading}[6]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
      \textit{\small#5} & \textit{\small #6} \\
    \end{tabular*}\vspace{-5pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeOrganizationHeading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textit{\small #2} \\
      \textit{\small#3}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%---------- HEADING ----------

\begin{center}
    \textbf{\Huge \scshape Pushkar Yadav} \\ \vspace{3pt}
    \small
    \faMobile \hspace{.5pt} \href{tel:918278622243}{+918278622243}
    $|$
    \faAt \hspace{.5pt} \href{mailto:pushkaryadavin@gmail.com}{pushkaryadavin@gmail.com}
    $|$
    \faLinkedinSquare \hspace{.5pt} \href{https://www.linkedin.com/in/pushkarydv/}{LinkedIn}
    $|$
    \faGithub \hspace{.5pt} \href{http://github.com/pushkarydv}{GitHub}
    $|$
    \faGlobe \hspace{.5pt} \href{https://pushkaryadav.in}{Portfolio}
    $|$
    \faMapMarker \hspace{.5pt} \href{https://www.google.com/maps/place/new+delhi+india/data=!4m2!3m1!1s0x390cfd5b347eb62d:0x52c2b7494e204dce?sa=X&ved=1t:155783&ictx=111}{New Delhi, India}
\end{center}


\section{About}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{

        \textbf{}{ I'm a Product-Driven Full-Stack Developerwith a passion for building innovative solutions, designing scalable architectures, and continuously expanding technical expertise. Experienced in the full product lifecycle, from ideation and development to SEO and marketing, with a portfolio spanning 16+ successful products serving 15,000+ users.
        }

    }}
    \resumeSubHeadingListEnd



%----------- SKILLS -----------

\section{Skills}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{
    
       
         \textbf{Languages, Frameworks:}{ JavaScript, CSS, C, HTML, Markdown, NextJS, ReactJS, TailwindCSS, Bootstrap, Framer, Material UI, Figma, SASS, Firebase, MongoDB, NodeJS, ExpressJS, Prisma, NPM, Git, GitHub, Langchain, Pinecone, AI Integrations} \\ \vspace{3pt}
        
        \textbf{Other:}{ Project Management, Collabrative Work,Team Leadership (GDSC LEAD) } \\ \vspace{3pt}
        
        
    }}
  \resumeSubHeadingListEnd



%----------- EXPERIENCE -----------

\section{Experience}
\resumeSubHeadingListStart

\resumeSubheading{Zura Ventures}{India / Remote}
{Full Stack Intern}{Apr 2023 -- Aug 2023}
\resumeItemListStart
\resumeItem{Developed revenue-generating B2B Shopify apps, including GiftKart, Easy Bundles, and Kite Free Gift, resulting in significant sales increases.}
\resumeItem{Collaborated with cross-functional teams, implemented features, resolved issues, and optimized performance using Next JS, Redis, GraphQL, Koa, and Shopify API.}
\resumeItemListEnd

\resumeSubheading{Cosmofeed}{India / Remote}
{Software Engineering Intern}{Nov 2022 -- Dec 2022}
\resumeItemListStart
\resumeItem{Contributed to a pre-release bio link app website, enhancing user experience and data gathering for potential customers.}
\resumeItemListEnd

\resumeSubheading{Leadership \& Community}{On-Site \& Remote}
{Various Roles}{Dec 2021 -- Present}
\resumeItemListStart
\resumeItem{Served as Google DSC Lead, GDSC Web Lead, and Hacktoberfest Maintainer, managing teams and promoting coding best practices.}
\resumeItem{Contributed as a Community Photography with 250k+ views, showcasing creativity and communication skills.}
\resumeItemListEnd

\resumeSubheading{Open-Source \& Personal Projects}{Remote}
{Freelance Developer}{Dec 2021 -- Present}
\resumeItemListStart
\resumeItem{Created and maintained open-source apps with 15,000+ users, solving technical problems and simplifying development tasks.}
\resumeItem{Contributed to open-source projects, showcasing version control, code review, and collaborative development skills, from ideation to deployment conquiring each small step SEO, LCP, Client Optimization and more.}
\resumeItemListEnd

\resumeSubHeadingListEnd



%----------- AWARDS & ACHIEVEMENTS -----------

\section{Awards \& Achievements}
  \vspace{2pt}
  \resumeSubHeadingListStart
    \small{\item{

        \textbf{LeanIn Hack IGDTUW 5.0 Top Team}{ Developed the Sakhi app, aimed at empowering women and promoting gender equality. (Feb 2024)}

        \textbf{HackJNU 3.0 Finalists}{ Created an innovative UN SDG-focused app, addressing sustainable development goals. (Jan 2024)}

        \textbf{Top 5 - IITB Techfest}{ Developed 'Mernifier,' a MERN Stack assistant, showcasing multi dimensnional model powered by pinecone, langchain, OpenAI and several other modern world technologies. (Dec 2023)}

        \textbf{Hackathon Winner}{Organised by Major League Hacking (June 2022)}

        \textbf{5th Product of the day}{ MDB (mdb.pushkaryadav.in) recognized by ProductHunt. (March 2021)}
    }}
  \resumeSubHeadingListEnd



%----------- PROJECTS -----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading{\textbf{Message Gator} $|$ \emph{\href{https://mg.writewrap.in}{mg.writewrap.in}}}{}
\resumeItemListStart
\resumeItem{Developed an innovative SaaS platform for real-time message/review integration, enabling businesses to manage multiple customizable widgets and seamlessly integrate with a proprietary library. Implemented features for converting reviews into social media-optimized images (Notez integration), enabling direct mail replies with context, and more.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{Notez} $|$ \emph{\href{https://notez.writewrap.in}{notez.writewrap.in}}}{}
\resumeItemListStart
\resumeItem{Designed and built a user-friendly note-taking application with a focus on shareability and customization. Key features include creating shareable links and notes with various theme customizations, as well as downloading attention-grabbing, social media-ready images to drive engagement.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{Mernifier} $|$ \emph{\href{https://mernifier.itsvg.in}{mernifier.itsvg.in}}}{}
\resumeItemListStart
\resumeItem{Developed an AI-powered coding assistant leveraging cutting-edge technologies such as Pinecone (custom-trained on millions of tokens from a self-generated dataset), LangChain, OpenAI, and Gemini. Mernifier provides accurate and up-to-date responses on modern web technologies like Next.js 14, surpassing the capabilities of ChatGPT.}
\resumeItemListEnd

\resumeProjectHeading{\textbf{Sakhi} $|$ \emph{\href{https://github.com/vishwaGauravIn/sakhi}{github.com/vishwaGauravIn/sakhi}}}{}
\resumeItemListStart
\resumeItem{Worked on Sakhi, a mobile-first app tailored for women, encompassing daily journals, safety features, community, and holistic health tools. Sakhi empowers and supports women's well-being through features like a menstrual tracker, mood journal, emergency SOS, community forum, Sakhi chatbot, fact-checking, menstrual knowledge, self-defense tutorials, and locating nearby hospitals and police stations. Aligned with UN SDGs for Good Health and Well-being, Reduced Inequalities, and Gender Equality.}
\resumeItemListEnd

\resumeItem{Additional projects showcasing a diverse range of skills and technologies can be found on my GitHub (\href{https://github.com/pushkarydv}{github.com/pushkarydv}) and professional portfolio (\href{https://pushkaryadav.in}{pushkaryadav.in}).}

\resumeSubHeadingListEnd


%-------------------------------------------
\end{document}